---
title: "Nanosight Analysis"
author: "Sean Nguyen"
output:
  html_document: default
  html_notebook: default
  pdf_document: default
---
#Overall Objective



##Load Libraries

```{r, echo=TRUE, message=FALSE, warning=FALSE}
library(tidyverse)
library(cowplot)
library(broom)
library(pwr)
```

##Import data
```{r, echo=TRUE, message=FALSE, warning=FALSE}
setwd("~/GitHub/time-course/data")

rawdata <- "revised_MASTER-ExperimentSummary.csv"
timecourse <- "timecourse2017.csv"


data <- read_csv(rawdata)
tc <- read_csv(timecourse, na = c("","NA"))
```

##Convert data from 'wide' to 'long' format
```{r, message=FALSE, warning=FALSE}
data1 <- data %>%
  gather(Sample,Count,2:226)

# Separate samples by identifiers 
data2 <- data1 %>% 
  separate(Sample, into=c("Sample_ID","Dilution_factor","Injection","Tech_rep", sep = "_")) %>% 
  select(-`_`)
```

##Factor the data into categorical variables

```{r}
# Refactoring Columns for samples
data2$Sample_ID <- as.factor(data2$Sample_ID)
data2$Dilution_factor <- as.numeric(data2$Dilution_factor)
data2$Injection<- as.factor(data2$Injection)
data2$Tech_rep <- as.numeric(data2$Tech_rep)


# Refactoring COlumns for timecourse
tc$Sample_ID <- as.factor(tc$Sample_ID)
tc$Day <- as.factor(tc$Day)
tc$Weight <- as.numeric(tc$Weight)
tc$TEI_Day <- as.factor(tc$TEI_Day)
```


```{r}
tc1 <- tc %>% 
  select(Day:Pups)
tc1
```

##Back calculate the original concentration of the sample
```{r}
data2 <- data2 %>% 
  mutate(True_Count=Dilution_factor*Count)
data2
```

## Average the three technical replicate readings
```{r, message=TRUE, warning=FALSE}
data3 <- data2 %>% 
  group_by(particle_size,Sample_ID,Dilution_factor,Injection) %>% 
  summarise( tech_N = length(True_Count),
             tech_mean = mean(True_Count),
             tech_sd = sd(True_Count),
             tech_se = tech_sd/sqrt(tech_N))
data3


test1 <- left_join(tc1,data3, by= "Sample_ID")
```


##Summarize samples by injection (average both injections)
```{r, warning=FALSE}

data4 <- data3 %>% 
  group_by(particle_size,Sample_ID,Dilution_factor) %>% 
  summarise( inj_N = length(tech_mean),
             inj_mean = mean(tech_mean),
             inj_sd = sd(tech_mean),
             inj_se = inj_sd/sqrt(inj_N))
data4

test2 <- left_join(tc1,data4, by= "Sample_ID")

test2

```

#Quick visualizations

### Graphing all samples
```{r, warning=FALSE}
test1$Sample_ID_correct = factor(test1$Sample_ID, levels=c('1','2','3','4','5','6','7','8','9','10','11','12','13','14','15','16','17','18','19','20','21','22','23','24','25','26','27','28','29','30','31','32','33','34','35','36'))

graph1 <- test1 %>%
  ggplot(aes(x=particle_size, y=tech_mean,color=Injection ))+ #plot
  geom_ribbon(aes(ymin=tech_mean-tech_se, ymax=tech_mean+tech_se),alpha=0.2,fill = alpha('grey12', 0.2)) + #error bars
  geom_line(size=2.0) + xlim(0,500)+ #line size, x-axis scale
  scale_y_continuous(expand=c(0,0))+ #set bottom of graph
  xlab("Particle Size") + # X axis label
  ylab("\nMean Particle Concentration/ml\n") + # Y axis label
  ggtitle("Nanosight Histogram of\nVirgin Mouse Plasma")+ #title
  labs(color="Injection")+ #Label table title
  facet_wrap( ~ Sample_ID_correct, nrow=6)

graph1
```

### Graphing averaged samples by experimental day
```{r, warning=FALSE}
graph2 <- test2 %>%
  group_by(TEI_Day) %>% 
  ggplot(aes(x=particle_size, y=inj_mean,color=Day ))+ #plot
  #geom_ribbon(aes(ymin=inj_mean-inj_se, ymax=inj_mean+inj_se),alpha=0.2,fill = alpha('grey12', 0.2)) + #error bars
  geom_line(size=2) + xlim(0,500)+ #line size, x-axis scale
  scale_y_continuous(expand=c(0,0))+ #set bottom of graph
  xlab("Particle Size") + # X axis label
  ylab("\nMean Particle Concentration/ml\n") + # Y axis label
  ggtitle("Nanosight Histogram of\nVirgin Mouse Plasma")+ #title
  labs(color="Condition")+ #Label table title
  facet_wrap(~ TEI_Day, ncol=6)

graph2
```
### Particle concentration values for each of the 36 samples
```{r}
test3 <- test2 %>% 
  group_by(Day,Sample_ID) %>% 
  summarise(particle_conc=sum(inj_mean))
test3
```
### Summary statistics of particle concentration (averaging n=6 for each time point)
```{r}
test4 <- test3 %>% 
  group_by(Day) %>% 
  summarise(Day_N=length(particle_conc),
            Day_mean = mean(particle_conc),
            Day_sd = sd(particle_conc),
            Day_se = Day_sd/sqrt(Day_N))
```

###Boxplot
```{r, warning=FALSE}
plot1 <- test3 %>% 
  group_by(Day) %>% 
  ggplot(aes(factor(Day),particle_conc, color=Day)) +
  geom_boxplot(colour="black",fill=NA) + 
  geom_point(position='jitter',size=3)+
  xlab("\nDay of Gestation\n") + # X axis label
  ylab("\nExosomes/ml\n") + # Y axis label
  ggtitle("Plasma Exosome Concentration\nThroughout Pregnancy\n")+ #title
  labs(color="Condition")#Label table title
plot1
```

###Bar plot
```{r, warning=FALSE}
plot <- test4 %>% 
  ggplot(aes(x=Day, y=Day_mean, fill=Day ))+ #plot
  geom_col()+
  geom_errorbar(aes(ymin=Day_mean-Day_se, ymax=Day_mean+Day_se), width=.5, 
                size=0.8, colour="black", position=position_dodge(.9)) + #error bars
  scale_y_continuous(expand=c(0,0))+ #set bottom of graph
  xlab("\nDay of Gestation\n") + # X axis label
  ylab("\nExosomes/ml\n") + # Y axis label
  ggtitle("Plasma Exosome Concentration\nThroughout Pregnancy\n")+ #title
  labs(color="Condition")#Label table title
plot
```

###Looking at Variation between the days the samples were run
```{r, warning=FALSE}
test7 <- test3 %>% 
  left_join(tc1)

plot2 <- test7 %>%
  ggplot(aes(x = Day, y = particle_conc, color = Day, shape=TEI_Day))+
  geom_point(position= 'dodge',size=4)+
  scale_shape_manual(values=c(15,16,17,22,23,24))+
  xlab("\nDay of Gestation\n") + # X axis label
  ylab("\nExosomes/ml\n") + # Y axis label
  ggtitle("Plasma Exosome Concentration\nThroughout Pregnancy\n")+ #title
  labs(color="Condition")#Label table title

plot2

```

#Statistics


###Shapiro test
```{r}
tidy(shapiro.test(test3$particle_conc))

```
p value >0.05 therefore conlude data is normally distributed

###ANOVA
```{r}
fit <- aov(particle_conc ~ Day, data=test3)
stats <- tidy(fit)
stats
```
Statistically significant, thus Tukey's HSD post hoc analysis can determine significant differences.

###Tukey Post Hoc Test
```{r}
HSD <- TukeyHSD(fit)
tukey <- tidy(HSD)
tukey
```

###Significant Tukey Post Hoc Test Values
```{r}
tukey %>%
  filter(adj.p.value<0.05) %>% 
  arrange(adj.p.value)
```


