---
title: "Standards Analysis"
author: "Sean Nguyen"
output: html_notebook
---


```{r, message=FALSE, warning=FALSE}
library(tidyverse)
library(cowplot)
library(broom)
```

###Set Working Directory
```{r, message=FALSE, warning=FALSE}
setwd("~/GitHub/time-course/data")
```
###Import data
```{r}
V2standards <- "day4_V2_std_reanalysis-ExperimentSummary.csv"
v2std <- read_csv(V2standards)
v2std
```
###Convert data from 'wide' to 'long' format and factor columns to 'categorica' variables
```{r, message=FALSE, warning=FALSE}
 re_std1 <- v2std %>% 
  gather(Sample,Count,2:73)

re_std2 <- re_std1 %>% 
  separate(Sample, into=c("Sample_ID","When","Dilution_factor","Nano_day","Injection","Tech_Rep", sep = "_")) %>% 
  select(-`_`)

str(re_std2)
re_std2$Sample_ID <- as.factor(re_std2$Sample_ID)
re_std2$When <- as.factor(re_std2$When)
re_std2$Dilution_factor <- as.numeric(re_std2$Dilution_factor)
re_std2$Injection<- as.factor(re_std2$Injection)
re_std2$Nano_day <- as.numeric(re_std2$Nano_day)
str(re_std2)
```
###Back Calculate
```{r}
re_std2 <- re_std2 %>% 
  mutate(True_Count=Dilution_factor*Count)

re_std2$Nano_day <-  factor(re_std2$Nano_day, levels=c('1','2','3','4','5','6'))
re_std2$When <- factor(re_std2$When, levels=c('before','after'))
```
###Summarize three technical replicates
```{r}
re_std3 <- re_std2 %>% 
  group_by(particle_size,Sample_ID,When,Dilution_factor,Nano_day,Injection) %>% 
  summarise( tech_N = length(True_Count),
             tech_mean = mean(True_Count),
             tech_sd = sd(True_Count),
             tech_se = tech_sd/sqrt(tech_N))
re_std3
```
###Summarize by injection
```{r}
re_std4 <- re_std3 %>% 
  group_by(Nano_day,When,particle_size) %>% 
  summarise( inj_N = length(tech_mean),
             inj_mean = mean(tech_mean),
             inj_sd = sd(tech_mean),
             inj_se = inj_sd/sqrt(inj_N))
re_std4

```

###Plot before and after plots, facet by experimental day
```{r}
redo_std <- re_std4 %>% 
  ggplot(aes(x=particle_size,y=inj_mean,color=When))+
  geom_ribbon(aes(ymin=inj_mean-inj_se, ymax=inj_mean+inj_se),alpha=0.2,fill = alpha('grey12', 0.2)) + #error bars
  geom_line(size=2) + xlim(0,500)+ #line size, x-axis scale
  scale_y_continuous(expand=c(0,0))+ #set bottom of graph
  xlab("Particle Size") + # X axis label
  ylab("\nMean Particle Concentration/ml\n") + # Y axis label
  ggtitle("Nanosight Histogram of\nVirgin Mouse Plasma")+ #title
  labs(color="Condition")+ #Label table title
  facet_grid(. ~ Nano_day)
redo_std

```
###Plot facet by when and experimental day
```{r}
redo_std2 <- re_std4 %>% 
  ggplot(aes(x=particle_size,y=inj_mean,color=When))+
  geom_ribbon(aes(ymin=inj_mean-inj_se, ymax=inj_mean+inj_se),alpha=0.2,fill = alpha('grey12', 0.2)) + #error bars
  geom_line(size=2) + xlim(0,500)+ #line size, x-axis scale
  scale_y_continuous(expand=c(0,0))+ #set bottom of graph
  xlab("Particle Size") + # X axis label
  ylab("\nMean Particle Concentration/ml\n") + # Y axis label
  ggtitle("Nanosight Histogram of\nVirgin Mouse Plasma")+ #title
  labs(color="Condition")+ #Label table title
  facet_grid(When ~ Nano_day)
redo_std2

```

###Particle concentrations from each experimental day
```{r}
redo_std_df <- re_std4 %>% 
  group_by(Nano_day,When) %>% 
  summarise(total=sum(inj_mean))
redo_std_df
```

###Bar graph of particle concentrations
```{r}
redo_std_df %>% 
  ggplot(aes(x=Nano_day,y=total,fill=When))+
  geom_col(position="dodge")+
  scale_y_continuous(expand=c(0,0))+ #set bottom of graph
  xlab("Experimental Day") + # X axis label
  ylab("\nMean Particle Concentration/ml\n") + # Y axis label
  ggtitle("Nanosight Histogram of\nVirgin Mouse Plasma")+ #title
  labs(color="When") #Label table title
```
###Intraassay variability
```{r}
Intra.assay_cv <- redo_std_df %>% 
  group_by(Nano_day) %>% 
  summarise(Day_N = length(total),
             Day_mean = mean(total),
             Day_sd = sd(total),
             Day_se = Day_sd/sqrt(Day_N),
            Day_cv = Day_sd/Day_mean )
Intra.assay_cv
```

###Inter assay variability
```{r}
Intra.assay_cv %>% 
  summarise(Exp_day= length())
```

