---
title: "Mouse Pregnancy Plasma Exosome Time Course"
author: "Sean Nguyen"
output:
  html_notebook: default
  pdf_document: default
---

#Introduction

#Experimental Design
Six animals will be use for six different time points throughout pregnancy



```{r  load_packages, include=FALSE}
library(tidyverse)
library(cowplot)
library(broom)
```



#Importing your data
This section will demonstrate how to get started with analyzing data using R.

**You will first want to tell R where to find all of your files, you can do this with the "setwd" command**  
- This is where R will read in all of your files and output your data that you generate(plots, CSVs, etc)  

**You can abbreviate long filenames by calling it an object, in this case we can make our long csv = "my data"**  
- This way you can just use "mydata" and it will automatically insert the filename  

**Next we will want to import the csv into r and we can accomplish this with the "read_csv" function**  
- This will import our csv file and we can make this an object known as "data"  
- Anytime we want to see the dataframe we can simply run "data"

```{r}
setwd("~/Library/Mobile\ Documents/com~apple~CloudDocs/time-course/")

rawdata <- "MASTER-ExperimentSummary.csv"
timecourse <- "timecourse2017.csv"

data <- read_csv(rawdata)
tc <- read_csv(timecourse, na = c("","NA"))

```

&nbsp;
We can quickly look at the dimensions of the dataframe with **dim()**
&nbsp;
```{r}
dim(data)
dim(tc)
```

&nbsp;
We can see the top of the dataframe with **head()**
&nbsp;
```{r}
head(data)
```

&nbsp;
You can also look at the bottom with **tail()**
&nbsp;

```{r}
tail(data)
```

#Convert data from wide type to long
```{r}
data1 <- data %>%
  gather(Sample,Count,2:223)


```

#Separate samples by identifiers 

```{r}
data2 <- data1 %>% 
  separate(Sample, into=c("Sample_ID","Dilution_factor","Injection","Tech_rep", sep = "_")) %>% 
  select(-`_`)
```

#Data types
R works with a variety of different data structures including, strings, vectors, factors, lists, integers, numerics and characters.   
What I found that works for me is to think of factors and categorical variables.

We can inspect the structure of the data type
```{r}
str(data2)
```
&nbsp;
&nbsp;

#Fixing data types
We can fix the data types to make things a factor (typically categorical variables) or numeric for numbers
The typical way to reformat data types is to call the data and specify the column name using **dataframe_name$column_name**  
Next you need to assign the column name **as.factor()** or **as.numeric()**, be sure to make sure the column is specified  
Then you will want to make **as.factor()** or **as.numeric()** equal to the column that you are changing 
&nbsp;
```{r}
data2$Sample_ID <- as.factor(data2$Sample_ID)
data2$Dilution_factor <- as.numeric(data2$Dilution_factor)
data2$Injection<- as.factor(data2$Injection)
data2$Tech_rep <- as.numeric(data2$Tech_rep)
```
&nbsp;
&nbsp;
Afterwards, be sure to check the data structure to make sure you did things correctly using the **str()**
```{r}
str(data2)
```

#Back-Calculate
```{r}
data2 <- data2 %>% 
   mutate(True_Count=Dilution_factor*Count)
```


&nbsp;
We can use **group_by()** to effectively 'lock' in certain variables/factors within a particular column.  In our case we will use group_by to 'lock' the particle_size, dilution factor and injection columns.  
&nbsp;  
**mutate()**is a command that will create a new column, the name of the column comes first and then whatever you want the column to be comes afterwards.  Example code ```data %>%  mutate(new_column_name=column1*column2)```  
&nbsp;  
Next we can use  **summarise()** to calculate the  number of rows within a certain group, calculate the average, standard deviation and standard error of the mean.
&nbsp;
```{r}
data3 <- data2 %>% 
  group_by(particle_size,Sample_ID,Dilution_factor,Injection) %>% 
  summarise( tech_N = length(True_Count),
             tech_mean = mean(True_Count),
             tech_sd = sd(True_Count),
             tech_se = tech_sd/sqrt(tech_N))
data3
```
&nbsp;  

#Refactoring to get the sample ID in the correct order
We can explicitly change the order of levels in a factor by telling R to do so.  
In order to do this, you have to specify what dataframe you want, in our case we will specify "data3" and the "Sample_ID" column.  In R, we designate columns with ```$```. The general formula is ```dataframe$column <- factor(dataframe$column, levels=c("First","Second","Third","Last"))```  

```{r}

str(tc)
tc$Sample_ID <- as.factor(tc$Sample_ID)
tc$Day <- as.factor(tc$Day)
tc$Weight <- as.numeric(tc$Weight)

tc1 <- tc %>% 
  select(Day:Pups)


str(tc1)
```


```{r}
test1 <- inner_join(tc1,data3, by= "Sample_ID")
```

#Summarize samples by injection
We can repeat **summarise()** again but on data3  to summarize the three readings to get one central reading  
We can make this new summarization = data4
&nbsp;
```{r}
data4 <- data3 %>% 
  group_by(particle_size,Sample_ID,Dilution_factor) %>% 
  summarise( inj_N = length(tech_mean),
             inj_mean = mean(tech_mean),
             inj_sd = sd(tech_mean),
             inj_se = inj_sd/sqrt(inj_N))
data4
```
&nbsp;
```{r}
test2 <- left_join(tc1,data4, by= "Sample_ID")
```


#Graphing data
Now that the data is structured properly we can graph the data to get an idea of what is going on.  
We will use the **ggplot()**
&nbsp;  
```{r warning=FALSE}
graph1 <- test1 %>%
  ggplot(aes(x=particle_size, y=tech_mean,color=Injection ))+ #plot
  geom_ribbon(aes(ymin=tech_mean-tech_se, ymax=tech_mean+tech_se),alpha=0.2,fill = alpha('grey12', 0.2)) + #error bars
  geom_line(size=2.0) + xlim(0,500)+ #line size, x-axis scale
  scale_y_continuous(expand=c(0,0))+ #set bottom of graph
  xlab("Particle Size") + # X axis label
  ylab("\nMean Particle Concentration/ml\n") + # Y axis label
  ggtitle("Nanosight Histogram of\nVirgin Mouse Plasma")+ #title
  labs(color="Injection")+ #Label table title
  facet_grid(. ~ Sample_ID)
graph1
```

&nbsp;
Next we can graph **data4** 
&nbsp; 

```{r warning=FALSE}
graph2 <- data4 %>% 
  ggplot(aes(x=particle_size, y=inj_mean,color=Sample_ID ))+ #plot
  geom_ribbon(aes(ymin=inj_mean-inj_se, ymax=inj_mean+inj_se),alpha=0.2,fill = alpha('grey12', 0.2)) + #error bars
  geom_line(size=2) + xlim(0,500)+ #line size, x-axis scale
  scale_y_continuous(expand=c(0,0))+ #set bottom of graph
  xlab("Particle Size") + # X axis label
  ylab("\nMean Particle Concentration/ml\n") + # Y axis label
  ggtitle("Nanosight Histogram of\nVirgin Mouse Plasma")+ #title
  labs(color="Condition")+ #Label table title
  facet_grid(. ~ Sample_ID)
graph2

```

&nbsp;
Next we can create a publication Quality figure by combining both graph1 and graph2 using the  **plot_grid()** function from the cowplot library.
&nbsp; 

```{r warning=FALSE}
plot_grid(graph1,graph2, labels = c("Individual\nInjections","Averaged"),nrow = 2, align = "v")
```

```{r warning=FALSE}
test3 <- test2 %>% 
  group_by(Day,particle_size) %>% 
  summarise(animal_N=length(Sample_ID),
            animal_mean = mean(inj_mean),
             animal_sd = sd(inj_mean),
             animal_se = animal_sd/sqrt(animal_N))

test3 %>% 
  ggplot(aes(x=Day, y=animal_mean,color=Day))+
  geom_col()

```



```{r warning=FALSE}
test4 <- test3 %>% 
  group_by(Day) %>% 
  summarise(particle_conc=sum(animal_mean))

test4 %>% 
  ggplot(aes(x=Day, y=particle_conc,fill=Day))+
  geom_bar(stat="identity")

```



```{r warning=FALSE}
test5 <- test2 %>% 
  filter(!Sample_ID=="15") %>% 
  group_by(Day,Sample_ID) %>% 
  summarise(particle_conc=sum(inj_mean))

test6 <- test5 %>% 
  filter(!Sample_ID=="15") %>% 
  group_by(Day) %>% 
  summarise(Day_N=length(particle_conc),
            Day_mean = mean(particle_conc),
             Day_sd = sd(particle_conc),
             Day_se = Day_sd/sqrt(Day_N))

write_csv(test5,"~/Library/Mobile\ Documents/com~apple~CloudDocs/time-course/particle_counts.csv")
write_csv(test6,"~/Library/Mobile\ Documents/com~apple~CloudDocs/time-course/particle_summary.csv")
write_csv(stats,"~/Library/Mobile\ Documents/com~apple~CloudDocs/time-course/ANOVA.csv")
write_csv(tukey,"~/Library/Mobile\ Documents/com~apple~CloudDocs/time-course/Tukey.csv")



plot1 <- test5 %>% 
  filter(!Sample_ID=="12") %>% 
  group_by(Day) %>% 
  ggplot(aes(factor(Day),particle_conc, color=Day)) +
  geom_boxplot(colour="black",fill=NA) + 
  geom_point(position='jitter')+
  xlab("\nDay of Gestation\n") + # X axis label
  ylab("\nExosomes/ml\n") + # Y axis label
  ggtitle("Plasma Exosome Concentration\nThroughout Pregnancy\n")+ #title
  labs(color="Condition")#Label table title


png("~/Library/Mobile\ Documents/com~apple~CloudDocs/time-course/particle_boxplot.png", width = 7, height = 5, units = 'in', res = 600)
plot1
dev.off()


jpeg("~/Library/Mobile\ Documents/com~apple~CloudDocs/time-course/particle_boxplot.jpg", width = 7, height = 5, units = 'in', res = 600)
plot1
dev.off()

plot <- test6 %>% 
 ggplot(aes(x=Day, y=Day_mean, fill=Day ))+ #plot
  geom_col()+
  geom_errorbar(aes(ymin=Day_mean-Day_se, ymax=Day_mean+Day_se), width=.5, 
      size=0.8, colour="black", position=position_dodge(.9)) + #error bars
  scale_y_continuous(expand=c(0,0))+ #set bottom of graph
  xlab("\nDay of Gestation\n") + # X axis label
  ylab("\nExosomes/ml\n") + # Y axis label
  ggtitle("Plasma Exosome Concentration\nThroughout Pregnancy\n")+ #title
  labs(color="Condition")#Label table title


png("~/Library/Mobile\ Documents/com~apple~CloudDocs/time-course/particle_summary.png", width = 7, height = 5, units = 'in', res = 600)
plot
dev.off()

```

```{r}
fit <- aov(particle_conc ~ Day, data=test5)


stats <- tidy(fit)

HSD <- TukeyHSD(fit)

tukey <- tidy(HSD)
```

